### 2015-11-13 postdoctoral/gamma_functions.tex
got nu product lemma

  \begin{theorem}
    If \(M\) is \(T_2\) or regular, then
    \(
      \varprojlim\{M,\nu,L\}\setminus\{\vect 0\}
        \cong
      (\check L\setminus\{\emptyset\})\times(M\setminus\{0\})
    \) with the usual product topology.
  \end{theorem}

  \begin{proof}
    Each point in \(\varprojlim\{M,\nu,L\}\setminus\{\vect 0\}\) is of the
    form \(\vect x_{A,m}\) where \(A\in\check L\setminus\{\emptyset\}\)
    and \(m\in M\setminus\{0\}\) defined by \(\vect x_{A,m}(l)=m\) for \(l\in A\)
    and \(x_{A,m}(l)=0\) otherwise.

    We claim that the bijection \(\theta(\vect x_{A,m})=\<A,m\>\) is a
    homeomorphism. Note that basic open sets of
    \(\varprojlim\{M,\nu,L\}\) are of the form \([U,F]\) where \(U(l)\) is
    an open subset of \(M\) for each \(l\in F\in[L]^{<\omega}\).

    Consider the point \(\<C,m\>\) in the basic open set \(V\times W\) in
    \((\check L\setminus\{\emptyset\})\times(M\setminus\{0\})\). Note that
    \(V\) is either of the form \((A,L]\) or \((A,B)\), and we may choose
    \(l_0\in C\setminus A\). We also may assume that \(W\) misses an open
    neighborhood \(Z\) of \(0\) as \(M\) is \(T_2\) or regular.
    In the case that \(V=(A,L]\) we let \(U(l_0)=W\).
    Then since \(l_0\in C\) and \(m\in W=U(l_0)\), it follows that
    \(\vect x_{C,m}\in[U,\{l_0\}]\).
    For any \(\vect x_{D,n}\in[U,\{l_0\}]\) we have that \(\vect x_{D,n}(l_0)=n\in W\);
    in particular, it's nonzero. So
    \(A\subsetneq (\leftarrow,l_0]\subseteq D\), putting \(D\in(A,L]=V\). Thus
    \(\theta(\vect x_{D,n})=\<D,n\>\in V\times W\).

@@

    On the other hand, consider the point \(\vect x_{C,m}\) in the basic
    open set \([U,F]\). It follows that \(m\in U(l)\) for all \(l\in C\cap F\),
    and \(0\in U(l)\) for all \(l\in F\setminus C\).

    TODO finish
  \end{proof}

>>>>

  \begin{lemma}
    If \(M\) is \(T_2\), then
    \(
      \varprojlim\{M,\nu,L\}\setminus\{\vect 0\}
        \cong
      (\check L\setminus\{\emptyset\})\times(M\setminus\{0\})
    \) with the usual product topology.
  \end{lemma}

  \begin{proof}
    Each point in \(\varprojlim\{M,\nu,L\}\setminus\{\vect 0\}\) is of the
    form \(\vect x_{C,m}\) where \(C\in\check L\setminus\{\emptyset\}\)
    and \(m\in M\setminus\{0\}\) defined by \(\vect x_{C,m}(l)=m\) for \(l\in C\)
    and \(x_{C,m}(l)=0\) otherwise.

    We claim that the bijection \(\theta(\vect x_{C,m})=\<C,m\>\) is a
    homeomorphism. Note that basic open sets of
    \(\varprojlim\{M,\nu,L\}\) are of the form \([U,F]\) where \(U(l)\) is
    an open subset of \(M\) for each \(l\in F\in[L]^{<\omega}\).

    Consider the point \(\<C,m\>\) in the basic open set \(V\times W\) in
    \((\check L\setminus\{\emptyset\})\times(M\setminus\{0\})\). Note that
    \(V\) is either of the form \((A,L]\) or \((A,B)\), and we may choose
    \(l_0\in C\setminus A\). We also may assume that \(W\) misses an open
    neighborhood \(Z\) of \(0\) as \(M\) is \(T_2\).

    In the case that \(V=(A,L]\) we let \(U(l_0)=W\).
    Then since \(l_0\in C\) and \(m\in W=U(l_0)\), it follows that
    \(\vect x_{C,m}\in[U,\{l_0\}]\).
    For any \(\vect x_{D,n}\in[U,\{l_0\}]\) we have that \(\vect x_{D,n}(l_0)=n\in W\);
    in particular, it's nonzero. So
    \(A\subsetneq (\leftarrow,l_0]\subseteq D\), putting \(D\in(A,L]=V\). Thus
    \(\theta(\vect x_{D,n})=\<D,n\>\in V\times W\).

@@

    On the other hand, consider the point \(\vect x_{C,m}\) in the basic
    open set \([U,F]\) of
    \(\varprojlim\{M,\nu,L\}\setminus\{\vect 0\}\).
    It follows that \(m\in U(l)\) for all \(l\in F\cap C\),
    and \(0\in U(l)\) for all \(l\in F\setminus C\).

    If \(F\subseteq C\), then let \(l_0\) be the maximum element of \(F\) and
    \(U'=\bigcap_{l\in F}U(l)\). Note \(\<C,m\>\in((\leftarrow,l_0),L]\times U'\).
    So let \(\<D,n\>\in((\leftarrow,l_0),L]\times U'\). Since \(l_0\in D\),
    \(\vect x_{D,n}(l_0)=n\in U'\). Since \(n\not=0\), we have
    \(\vect x_{D,n}(l)=n\in U'\subseteq U(l)\) for all \(l\in F\), so
    \(\vect x_{D,n}\in[U,F]\).

    If \(F\cap C=\emptyset\), then
    let \(l_1\) be the minimum element of \(F\setminus C\).
    Note \(\<C,m\>\in(\emptyset,(\leftarrow,l_1])\times (M\setminus \{0\})\).
    So let \(\<D,n\>\in(\emptyset,(\leftarrow,l_1])\times (M\setminus \{0\})\).
    Since \(l_1\not\in D\), \(\vect x_{D,n}(l)=0\in U(l)\) for all \(l\in F\),
    giving \(\vect x_{D,n}\in[U,F]\).

    Otherwise, let \(l_0\) be the maximum element of \(F\cap C\) and
    \(l_1\) be the minimum element of \(F\setminus C\).
    Let \(U'\subseteq \bigcap_{l\in C\cap F}U(l)\) and
    \(U''\subseteq \bigcap_{l\in F\setminus C}U(l)\).
    Note \(\<C,m\>\in((\leftarrow,l_0),(\leftarrow,l_1])\times U'\).
    So let \(\<D,n\>\in((\leftarrow,l_0),(\leftarrow,l_1])\times U'\).
    Since \(l_0\in D\) and \(l_1\not\in D\), we have
    \(\vect x_{D,n}(l_0)=n\in U'\) and
    \(\vect x_{D,n}(l_1)=0\in U''\). Furthermore,
    \(\vect x_{D,n}(l)=n\in U'\subseteq U(l)\) for all \(l\in F\cap C\), and
    \(\vect x_{D,n}(l)=0\in U''\subseteq U(l)\) for all \(l\in F\setminus C\),
    so \(\vect x_{D,n}\in[U,F]\).
  \end{proof}
